Hydra Battles and Cie

### 2021-08-25 doc/part-hydras.tex
Alectryon:  chapter 7 (30%)

\begin{Coqsrc}
Reserved Notation "'F' n" (at level 29) .

Fixpoint finite (i:nat) : Ord :=
  match i with 
            | 0 => zero
            | S i => succ (F i)
  end
where "'F' i" := (finite i)  : schutte_scope.

Coercion finite : nat >-> Ord.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition is_lub (M:Type)
                  (D : Ensemble M)
                  (lt : relation M)
                  (X:Ensemble M)
                  (a:M) :=
   In _ D a  /\ upper_bound  D lt X a  /\
   (forall y, In _ D y -> upper_bound  D lt X y  -> 
                  y = a \/ lt a y).
\end{Coqsrc}

\begin{Coqsrc}
Definition sup_spec X lambda := is_lub ordinal lt X lambda.

Definition sup (X: Ensemble Ord) : Ord  := the  (sup_spec X).

Notation "'|_|' X" := (sup X) (at level 29) : schutte_scope.
\end{Coqsrc}

Then, we define the function \texttt{omega\_limit} which returns the least upper bound 
of the  (denumerable) range of any sequence \texttt{s: nat -> Ord}. 
By \texttt{AX3} this range is bounded, hence the set of its upper bounds is not empty and has a least element.

\begin{Coqsrc}
Definition omega_limit (s:nat->Ord) : Ord 
  := |_| (seq_range s).
\end{Coqsrc}

Then we define \texttt{omega} as the limit of the sequence of finite ordinals.

\label{sect:notation-omega}
\begin{Coqsrc}
Definition _omega := omega_limit finite.

Notation "'omega'" := (_omega) : schutte_scope.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma finite_lt_omega : forall i: nat,  i < omega.

Lemma lt_omega_finite alpha : Ord) : 
  alpha < omega ->  exists i:nat, alpha =  i.

Lemma is_limit_omega : is_limit omega.
\end{Coqsrc}

>>>>

\input{movies/snippets/Schutte_basics/finiteDef}

@@

\input{movies/snippets/Lub/isLubDef}

\input{movies/snippets/Schutte_basics/supDef}

Then, we define the function \texttt{omega\_limit} which returns the least upper bound 
of the  (denumerable) range of any sequence \texttt{s: nat -> Ord}. 
By \texttt{AX3} this range is bounded, hence the set of its upper bounds is not empty and has a least element.
Then we define \texttt{omega} as the limit of the sequence of finite ordinals.

\input{movies/snippets/Schutte_basics/omegaDef}

\label{sect:notation-omega}

@@

\input{movies/snippets/Schutte_basics/omegaProps}
